\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-07-06 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
acknowledge Geza Seriani and Enrico Priolo in the users manual

\noindent The SPECFEM3D Cartesian package was first developed by Dimitri
Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe
(IPGP) in Paris, France from 1995 to 1997 and then by Dimitri Komatitsch
and Jeroen Tromp at Harvard University and Caltech, USA, starting
in 1998. The story started on March 28, 1995, when Prof. Yvon Maday
from CNRS and University of Paris, France, gave a lecture to Dimitri
Komatitsch and Jean-Pierre Vilotte at IPG about the nice properties
of the spectral-element method that he had used for other equations.
We are deeply indebted and thankful to him for that.

>>>>

\noindent The SPECFEM3D Cartesian package was first developed by Dimitri
Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe
(IPGP) in Paris, France from 1995 to 1997 and then by Dimitri Komatitsch
and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998.
The story started on March 28, 1995, when Prof. Yvon Maday from CNRS and University of Paris, France, gave a lecture to
Dimitri Komatitsch and Jean-Pierre Vilotte at IPG about the nice properties of the Legendre spectral-element method with diagonal mass matrix that he had used for
other equations. We are deeply indebted and thankful to him for that.
That followed a visit by Dimitri Komatitsch to OGS (Istituto Nazionale di Oceanografia e di Geofisica Sperimentale) in Trieste, Italy, in February 1995
to meet with G\'eza Seriani and Enrico Priolo, who introduced him to their 2D Chebyshev version of the spectral-element method with a non-diagonal mass matrix.
We are deeply indebted and thankful to them for that.
